Phylogenetics and the human microbiome.

### 2013-04-02 sbreview.tex
more!

\forarxiv{
\end{abstract}
\maketitle

\section{Introduction}
}

@@

Starter paragraph about the scope of human microbiome research.

We will begin by introducing the results of recent research.
% There have been hundreds of papers concerning the human microbiome, and it is not our desire to survey all of these.
% Rather, our idea is to highlight areas that may be of particular interest for the phylogenetics community by potentially having wider applications or by being areas for future exploration.
% Please note that many of the methods and issues described in this paper will be equally useful for microbial ecology in general, but by narrowing our scope we were able to keep our paper within reasonable size limits.

The human microbiome has remarkable metabolic potential.
cite qin paper, and follow up

The microbiome is dynamic in terms of representation but apparently constant in terms of function.
cites

Human microbiome is spatially organized.
cite segre,

Inter-individual versus intra-individual variation.

@@

Substantial attention was given to whether microbial ``types'' exist.
A high-profile paper from Per Bork's group
http://www.nature.com/news/gut-microbial-enterotypes-become-less-clear-cut-1.10276

Important bacteria that were previously unknown?

\cite{hugenholtz2002review}
{{E}xploring prokaryotic diversity in the genomic era}

Major finding: antibiotics.
\cite{dethlefsen2008pervasive,dethlefsen2011incomplete,jakobsson2010short,jernberg2007long}
obesity
turnbaugh papers
http://www.nature.com/nature/journal/v444/n7122/abs/nature05414.html
http://europepmc.org/abstract/MED/18407065/reload=0;jsessionid=Ea4YLfXjd7Cfpx5Hvafq.2
amish study
http://precedings.nature.com/documents/4957/version/1

@@

% applications
\cite{costello2009bacterial}
Bacterial community variation in human body habitats across space and time

\cite{ley2006microbial}
Microbial ecology: human gut microbes associated with obesity
Terminology: survey versus metagenome.
definition of a single sample.

@@

GEBA. Most wanted.

>>>>

\forarxiv{
\end{abstract}
\maketitle
}

@@

Starter paragraph about the scope of human microbiome research.
Our idea is to highlight areas that may be of particular interest for the phylogenetics community by potentially having wider applications or by being areas for future exploration.

Terminology: survey versus metagenome.
Definition of a single sample.

The human microbiome is.
Virome.
Has been opened up by high-throughput sequencing.
Non-culturable organisms.

This sequencing has shown that the microbiome contains a diverse collection of organisms, has remarkable metabolic potential.
Number of species.
\cite{qin2010human}
% To understand the impact of gut microbes on human health and well-being it is crucial to assess their genetic potential. Here we describe the Illumina-based metagenomic sequencing, assembly and characterization of 3.3 million non-redundant microbial genes, derived from 576.7 gigabases of sequence, from faecal samples of 124 European individuals. The gene set, ~150 times larger than the human gene complement, contains an overwhelming majority of the prevalent (more frequent) microbial genes of the cohort and probably includes a large proportion of the prevalent human intestinal microbial genes. The genes are largely shared among individuals of the cohort. Over 99% of the genes are bacterial, indicating that the entire cohort harbours between 1,000 and 1,150 prevalent bacterial species and each individual at least 160 such species, which are also largely shared. We define and describe the minimal gut metagenome and the minimal gut bacterial genome in terms of functions present in all individuals and most bacteria, respectively.

The microbiome is dynamic in terms of representation but apparently constant in terms of function.
\cite{hmp2012structure}

Human microbiome is spatially organized, as can be seen on skin \cite{grice2009topographical}.

Inter-individual versus intra-individual variation \cite{hmp2012structure}

@@

Substantial attention was given to whether microbial ``types'' exist.
A high-profile paper from Per Bork's group had enterotypes: Bacteroides, Prevotella or Ruminococcus.
\cite{arumugam2011enterotypes}
Appears that there is a real tendency to cluster around Bacteroides or Prevotella \cite{wu2011linking}

\cite{hugenholtz2002review}
{Exploring prokaryotic diversity in the genomic era}

Major finding: antibiotics.
\cite{dethlefsen2008pervasive,dethlefsen2011incomplete,jakobsson2010short,jernberg2007long}

obesity
turnbaugh papers
http://www.nature.com/nature/journal/v444/n7122/abs/nature05414.html
http://europepmc.org/abstract/MED/18407065/reload=0;jsessionid=Ea4YLfXjd7Cfpx5Hvafq.2
amish study
http://precedings.nature.com/documents/4957/version/1

@@

\cite{costello2009bacterial}
Bacterial community variation in human body habitats across space and time

\cite{ley2006microbial}
Microbial ecology: human gut microbes associated with obesity

@@

A phylogeny-driven genomic encyclopaedia of Bacteria and Archaea \cite{wu2009phylogeny}.

Most wanted.
